\documentclass[10pt]{article}

\usepackage[hmargin=1in,vmargin=0.25in]{geometry}

\usepackage{fontspec}
\setmainfont{Gill Sans}

\begin{document}

\pagestyle{empty}

\newsavebox{\debriefingtext}

\sbox{\debriefingtext}{%
  \begin{minipage}{1.0\linewidth}
    \bigskip
    \footnotesize
    \setlength{\parindent}{3ex}
    \begin{center}\small
      Rotation Experiment Debriefing
    \end{center}

    Thank you for volunteering to participate in this experiment.  The
    purpose is to investigate how people store and manipulate visual
    information in their minds.  Many previous studies have shown that men
    tend to perform better than women in the mental rotation task that you
    performed today.  However, other studies show that these differences
    disappear in various situations, including when people are told that
    women perform better than men.  Also, there are little to no sex
    differences in other visual-processing tasks.

    Half of the volunteers in this experiment were told that men are better
    than women in this task, and half were told the opposite.  We expect to
    find that the different instructions will reduce or eliminate sex
    differences in the task.  This study is part of a larger set of studies
    investigating whether these sex differences are due to fundamental
    differences in mental processing or more superficial differences in how
    men and women choose to perform the task.

    If you have any questions or concerns about this study, please contact
    Prof.\ David Fencsik by phone at 510-885-3484 or by email at
    \mbox{david.fencsik@csueastbay.edu}.

    Thank you again.

    \bigskip\bigskip

  \end{minipage}
}

\begin{center}
  \hrulefill

  \usebox{\debriefingtext}

  \hrulefill

  \usebox{\debriefingtext}

  \hrulefill

  \usebox{\debriefingtext}

  \hrulefill

  \usebox{\debriefingtext}

  \hrulefill
\end{center}


\end{document}

% Local Variables:
% TeX-engine: luatex
% End:
