\documentclass[10pt]{article}

\usepackage[hmargin=1in,vmargin=0.25in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{mathptmx}

\begin{document}

\pagestyle{empty}

\newsavebox{\debriefingtext}

\sbox{\debriefingtext}{%
  \begin{minipage}{1.0\linewidth}
    \bigskip
    \fontsize{8}{10}\selectfont
    \setlength{\parindent}{3ex}
    \begin{flushright}
      Spring 2014
    \end{flushright}
    \begin{center}\fontsize{10}{12}\selectfont
      Rotation Experiment Debriefing
    \end{center}

    Thank you for volunteering to participate in this experiment.  The
    purpose of this experiment is to investigate differences between men
    and women in spatial processing.  The mental rotation task you
    performed measures how well people can think about and manipulate
    objects.  A lot of research suggests that men tend to perform better at
    such tasks than women.

    We are trying to investigate specific causes of this difference between
    the sexes.  With the data you helped us collect, we will try to
    determine whether there is a difference in the act of manipulating an
    object in your head.  The results will be used by students for their
    class project.

    If you have any questions or concerns about this study, please contact
    Prof.\ David Fencsik by phone at 510-885-2384 or by email at
    david.fencsik@csueastbay.edu.  Thank you again.

    \bigskip\bigskip

  \end{minipage}
}

\begin{center}
  \hrulefill

  \usebox{\debriefingtext}

  \hrulefill

  \usebox{\debriefingtext}

  \hrulefill

  \usebox{\debriefingtext}

  \hrulefill

  \usebox{\debriefingtext}

  \hrulefill

  \usebox{\debriefingtext}

  \hrulefill
\end{center}


\end{document}
